---
title: "Data Products Week 2"
output: html_document
---

# Top Hiking Trails in Southern Afirca
### Date 2018-07-27
### Assignment
Create a web page using R Markdown that features a map created with Leaflet.
Host your webpage on either GitHub Pages, RPubs, or NeoCities.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Description
Size of Circles = Relative to the duration of the hike

Color of Circles = Hike difficulty according to KM's per day

Popup = Hike Name and URL including more information of the hike

### My Awesome Map
```{r, echo=FALSE, message=FALSE, warning=FALSE}
Trails <- c("The Otter Trail","Fish River Canyon Trail",
"The Whale Trail","Fanie Botha Trail","Amatola Trail",
"Giant's Cup Trail","Tankwa Camino Trail","Magoebaskloof Trail")

Lat <- c(-34.005463, -27.712883, -34.378219,
-25.094309, -32.889533, -29.731299, -32.241766, -23.828643)

Lon <- c(23.785833, 17.601088,
20.534697, 30.740088, 27.404803, 29.372663, 20.096136, 29.988061)

Distance <- c(42.5, 84, 55, 71.5, 100.3, 59.3, 256.6, 60)

Duration <- c(5, 4, 5, 5, 6, 5, 10, 5)

Url <- c("<a href='https://www.hikingsouthafrica.co.za/the-otter-trail/'>The Otter Trail</a>",
"<a href=https://www.hikingsouthafrica.co.za/fish-river-canyon-hiking-trail/'>Fish River Canyon</a>",
"<a href=https://www.hikingsouthafrica.co.za/whale-trail/'>The Whale Trail</a>",
"<a href=https://www.hikingsouthafrica.co.za/fanie-botha-hiking-trail/'>Fanie Botha Trail</a>",
"<a href=https://www.hikingsouthafrica.co.za/amatola-hiking-trail/'>Amatola Trail</a>",
"<a href=https://www.hikingsouthafrica.co.za/giants-cup-hiking-trail/'>Giants Cup</a>",
"<a href=https://www.tankwacamino.com/'>Tankwa Camino</a>",
"<a href=https://www.outdoorphoto.co.za/blog/forests-fireflies/'>Magoebaskloof Trail</a>")

Hiking_trails <- data.frame(Trails,Lon,Lat,Distance,Duration,Url)
Hiking_trails$km_day <- Hiking_trails$Distance/Hiking_trails$Duration

library(dplyr)
Hiking_trails <- mutate(Hiking_trails, colors = ifelse(km_day<15,"darkgreen",ifelse(km_day<20,"darkorange","darkred")))

#install.packages("leaflet")
library(leaflet)
my_map <- leaflet() %>% addTiles() %>% 
    addCircleMarkers(lat=Hiking_trails$Lat, 
               lng=Hiking_trails$Lon, 
               popup=Hiking_trails$Url,
               weight=1,
               radius=(Hiking_trails$Duration)*2,
               color= Hiking_trails$colors)
my_map
```

